---
title: "esm206_lab10"
author: "Abigail Sanford"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Attach Packages
library(tidyverse)
library(janitor)
library(usethis)

library(beepr)
library(praise)
library(cowsay)
library(sf)
library(paletteer)
```

## beepr::beep()
Beepr beeps: i.e. after the code is running it will give a beep sound

In the console you can write `beep(insert_#_btwn_1-12)` and get a preset sound!

beep(1)
beep(2)
beep(3)
beep(4)
beep(5)

Use `beep()` to give yourself an audio alert.

## Write a `for loop + beep`

song: 99 beer bottles on the wall
```{r, eval = FALSE}
for(i in rev(seq(1:9999))){print(paste(i, "bottles of beer on the wall"))}

beep(4) # if you don't want this to make a sound when you knit it, make sure to do eval = FALSE in the setup
```


the reverse `rev` and sequence `seq` functions will give us a sequence that will count backwards between the two numbers we tell it.

For each of these elements, we want it to print out a line from the song. we use `print(i)` to do that. and if we want additional text to be written, we can use `paste(i, "insert what you want written after the sequence here")`


## `praise` is nice

```{r}
praise("${EXCLAMATION}!!! This code works ${adverb_manner}!") # this is case sensitive. So if its all in caps, then it will follow that caps in the output.

praise("Holy ${creating}, Batman - this code works ${ADVERB_MANNER}!")
```


## `cowsay::say` to have animals say something

```{r}
say("I love tacos!") # default is cat

say("I love tacos!", by = "shark")

say("I love tacos!", by = "trilobite")
```


## `usethis` for everything

Can be used to update your r profile, and change what will show up everytime you start a new r session.










